Data Preparation, Integration and Cleaning

### 2017-02-08 abbDataPrep_Script.Rmd
adding host policy data clean

>>>>

#### Host Policies

Here we combine the two Strict (regular and super) cancellation policies into one as there are few 'super' strict and this is used as a factor in future modeling.  We also remove the few observations with missing host policy data

  ss60 <- which(str.data$cancel.policy == 'Super Strict 60 Days')
  str.data$cancel.policy[ss60] <- 'Strict'
  cpmiss <- which(str.data.ic$cancel.policy == '')
  str.data <- str.data[-cpmiss, ]
